README.md

### 2021-10-22 README.Rmd
readme update ☘️

# Seed germination ecology of European mesic grasslands

This repository stores all the information related to the manuscript *Seed germination ecology of European mesic grasslands*, including the raw datasets, the scripts to perform data cleaning and analysis, and the `Rmarkdown` files to create the manuscript.

@@

Please cite the dataset as `CITATION`

>>>>

# Seed ecology of European mesic grasslands

This repository stores all the information related to the manuscript *Seed ecology of European mesic grasslands*, including the raw datasets, the scripts to perform data cleaning and analysis, and the `Rmarkdown` files to create the manuscript.

@@

Please cite the dataset as `Fernández-Pascual E, Vaz M, Morais B, Reiné R, Ascaso J, Afif Khouri E, Carta A. Seed germination ecology of European mesic grasslands. Annals of Botany, in press.`
